%Define style
\documentclass[11pt,a4paper,final]{report}
%Set reduced margins
%\usepackage[margin=25mm]{geometry}
\usepackage{geometry}
\geometry{a4paper,
  twoside,
  margin=20mm,
  bindingoffset=20mm, %Extra margin on binding edge (must total 40mm)
  top=25mm, %Override top margin
  bottom=25mm, %Override bottom margin
  heightrounded,
}

% Use fancy headers
\usepackage{fancyhdr}
%\pagestyle{fancy}
\pagestyle{headings}

%Set line spacing to 1.5 except captions etc
\usepackage{setspace} 
%\doublespacing
\onehalfspacing

%Reduce font size for figure captions
\usepackage[font=small,labelfont=bf, textfont=it]{caption}

%Enable graphics
\usepackage{graphicx}

%Enable coloured text
\usepackage{xcolor}

%Enable floats (ie. aligning of multi-line equations)
\usepackage{float}

%Enable equations package
\usepackage{amsmath}

%Enable control over section numbering
\usepackage{titlesec}
\setcounter{secnumdepth}{3}

%Enable PDF links
\usepackage[hidelinks]{hyperref}

%Enable SI units package
\usepackage{siunitx}

%Enable multi-row tables
\usepackage{multirow}

%Enable inline references
\usepackage{bibentry}
\nobibliography*


%Define way to add matrix vertical line, used in 3D matrices and augmenting
\makeatletter
\renewcommand*\env@matrix[1][*\c@MaxMatrixCols c]{%
	\hskip -\arraycolsep
	\let\@ifnextchar\new@ifnextchar
	\array{#1}}
\makeatother

%Define way to add tensor dots
\def\onedot{$\mathsurround0pt\ldotp$}
\def\cddot{% two dots stacked vertically
	\mathbin{\vcenter{\baselineskip.67ex
		\hbox{\onedot}\hbox{\onedot}}%
	}}%
\def\cdddot#1{% three dots 
	\mathbin{\vcenter{\baselineskip.67ex
		\hbox{\onedot}\hbox{\onedot}\hbox{\onedot}%
	}}%
}

%Define hyphen in math mode
\mathchardef\mhyphen="2D

%Title and author info (REDUNDANT WITH CUSTOM TITLE PAGE)
\title{Thesis 2018}
\author{
	Collins, J.T. \\ 
	Department of Physics\\
	University of Bath\\
}

%Include build date
\date{\today}


%Control TOC size
\AtBeginDocument{
  \addtocontents{toc}{\normalsize}
  \addtocontents{lof}{\normalsize}
}

\begin{document}


% Custom title page
\begin{titlepage}
    \input{./title}
\end{titlepage}

% Abstract
\begin{abstract}
	\setcounter{page}{0}  % Fix the janky page numbering to get the correct binding-edge margin
    \input{./abstract}
\end{abstract}
\clearpage

\pagenumbering{arabic}  % Start normal page numbering
% Table of contents
\clearpage 
\tableofcontents
\clearpage


% Acknowledgements
\chapter*{Acknowledgements}
I would first like to thank Ventsislav Valev for his supervision, guidance, and motivation during the last three years. When I started this project our research group was just a few months old, and I am immensely proud of what we achieved in the following years. I have no doubt this is only the beginning. Of course, this would not have been possible without the work, support, and friendship of Christian Kuppe, David Hooper, and Kristina Rusimova; who made this group the best it could be, both professionally and personally. Additionally, I would like to thank all of those with whom I have had the privilege of collaborating during this time. In particular, I would like to thank Dimitar Slavov and Dave Carbery for their long-term academic support, interesting ideas, and invaluable friendship. I would also like to thank Peter Mosley and the rest of the CPPM for creating the best possible environment for new researchers from the day we all started. 

Besides those involved directly in our work, I would of course like to thank my family. For both emotional support over the last 26 years, and for helping immensely during the authoring of this thesis. I cannot thank you enough. I'd like to specifically single out my Grandma Sandra for the inspirational advice: ``If you feel yourself worrying, don't''; and my brother Dan for somehow knowing exactly how I was feeling, and what I needed, at all times. Likewise, I would like to thank Charlotte Parry for her immense support since we met. You have stuck by me through my best laid plans and my worst of ideas, and never once stopped supporting me. For reminding me in hard times that ``It doesn't really matter, does it?'', ``Just let it go, it's not worth it'', and that we ``Gotta go fast''. You have made this time infinitely more fantastic than it would have otherwise been.

I would like to thank Philip Madgwick for making my time in Bath both immensely interesting, and fun, and reminding me that there's a big wide world outside of just physics. Finally, I would like to thank Sam Bell for standing by me as my permanent temporary secretary. You came along and stayed a spell, and I will be forever grateful.

% Publications
\chapter*{Publications}

\bibentry{Lovesey2018}

\bigskip \noindent \bibentry{Rusimova2018}

\bigskip \noindent \bibentry{Collins2018c}

\bigskip \noindent \bibentry{Collins2018b}

\bigskip \noindent \bibentry{Kuppe2018}

\bigskip \noindent \bibentry{Collins2018}

\bigskip \noindent \bibentry{Collins2017}

\bigskip \noindent \bibentry{Hooper2017}


% Main text
\include{./sections/background/Introduction}
\include{./sections/background/Chirality}
\include{./sections/background/NonlinearOptics}
\include{./sections/background/Plasmonics}

\include{./sections/results/EnantiomorphingChiralCrosses}
\include{./sections/results/OAinPlanarNanohelices}
\include{./sections/results/HRSinLiquidNanohelices}

\include{./sections/Conclusions}

% Bibliography
%\bibliographystyle{unsrt}
\bibliographystyle{ieeetr}
\bibliography{library}
\clearpage

% Appendix
\appendix
\chapter{Reducing \texorpdfstring{$\chi^{(2)}$}{Lg} with Symmetry}\label{sec:appendix:rotations}
\input{./sections/appendix/RotIso}
\chapter{Equipment Details}\label{sec:appendix:Hardware}
\input{./sections/appendix/Hardware}
\chapter{Additional Data: Chiral Crosses}\label{sec:appendix:AdditionalCrosses}
\input{./sections/appendix/AdditionalCrosses}
\chapter{Additional Data: Au Nanohelices}\label{sec:appendix:AdditionalAuHelix}
\input{./sections/appendix/AdditionalHelixOR}
\chapter{Automated Data Acquisition and Analysis}\label{sec:appendix:Code}
\input{./sections/appendix/Code}

\end{document}